\tnoteref{note1}Training Feedforward Neural Networks with Bayesian Hyper-Heuristics

### 2023-02-09 article/main.tex
💚 Dedicated to Taylah, Beané and Aleah

\usepackage{acro}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{url}
\usepackage{subcaption}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{multirow}

@@

@@

	\begin{abstract}
		The process of training \acfp{FFNN} can benefit from an automated process where the best heuristic to train the network is sought out automatically by means of a high-level probabilistic-based heuristic. This research introduces a novel population-based \acf{BHH} that is used to train \acfp{FFNN}. The performance of the \acs{BHH} is compared to that of ten popular low-level heuristics, each with different search behaviours. The chosen heuristic pool consists of classic gradient-based heuristics as well as \acf{MH}. The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics. The \acs{BHH} is shown to be able to train \acp{FFNN} well and provide an automated method for finding the best heuristic to train the \acp{FFNN} at various stages of the training process.
	\end{abstract}

@@

A popular field of focus for studying \acfp{ANN} is the process by which these models are trained. \acp{ANN} are trained by optimisation algorithms known as heuristics. Many different heuristics have been developed and used to train \acp{ANN} \citep{ref:rakitianskaia:2012}. Each of these heuristics have different search behaviours, characteristics, strengths and weaknesses. Finding the best heuristic to train \acp{ANN} is required in order to yield optimal results. This process is often non-trivial and time-consuming. Selection of the best heuristic to train \acp{ANN} is often problem specific \citep{ref:allen:1996}.

@@

@@

This research focuses on a particular type of \acs{ANN}, referred to as \acfp{FFNN}. \acp{FFNN} were the first and simplest type of \acp{ANN} developed \citep{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order. Furthermore, \acp{FFNN} implement fully connected topologies, where each \acs{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles \citep{ref:zell:1994}. In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.

@@

Gradient-based heuristics are optimisation techniques that make use of derivatives obtained from evaluating the \acs{ANN} error function. In the context of supervised learning, loss functions produce a scalar value $\epsilon$, that represents the error between the output of the \acs{ANN} and the desired output. When using \acf{GD} to train \acp{ANN}, the gradients of the loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \citep{ref:engelbrecht:2007}.

There are many variants of gradient-based heuristics, however, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}. This algorithm is known as \acf{BP}. \acs{BP} was popularised by \citet{ref:werbos:1994}.

The simplest type of \acs{GD} algorithm is referred to as \acs{SGD}, which implements a gradient-based weight update step for each training pattern. In the context of this research, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}, where a small batch of training patterns are fed to the \acs{FFNN} at once and the error function is aggregated across all training patterns.

@@

Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus \citep{ref:bengio:2000}. \citet{ref:blum:2003} mention that since the 1980's, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space. These methods are referred to as \acp{MH}.

@@

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include \citep{ref:dowsland:2007, ref:burke:2010, ref:grobler:2012, ref:vanderstockt:2018}. Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce. \citet{ref:nel:2021} provides some of the first research in this field, applying an novel adaptation of an evolutionary-based \acs{HH}, known as the \acf{AMALGAM} \acs{HH} \citep{ref:vrugt:2007}, to \acs{FFNN} training. Furthermore, \citet{ref:oliva:2019} provide the \acf{HHBOA}, the first use of Bayesian optimisation in a \acs{HH} context. The method proposed by \citet{ref:oliva:2019} uses a Bayesian selection operator to evolve combinations of low-level heuristics  while looking for good problem solutions to a benchmark of optimisation functions, but does not apply a \acs{HH} to the training of \acp{FFNN}.

@@

Bayesian analysis utilises the concept of conjugate priors. \citet{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form, $\mathcal{A}(v)$, as the prior, but with different parameter values. The conjugate prior to a Bernoulli probability distribution is the Beta probability distribution and the conjugate prior to a Categorical and Multinomial probability distribution is the Dirichlet probability distribution \citep{ref:wackerly:2014}.

@@

This section presents the novel \acs{BHH}. The general concept of the \acs{BHH} can be summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics, to apply to a population of entities, each implementing a candidate solution to a \acs{FFNN}, with the intent of both optimising the underlying \acs{FFNN} and the \acs{FFNN} training process. The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process. These probabilities are then used as heuristic selection probabilities in the next step of the training process.

According to the classification scheme for \acp{HH} by \citet{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion.

Figure \ref{fig:bhh_architecture} provides an illustration of the high-level architecture of the \acs{BHH}. Algorithm \ref{algo:bhh} provides the high level pseudo-code implementation of the \acs{BHH}. Discussions follow on the most important components of the \acs{BHH}.

@@

		\If {step > replay window size}
		\State prune performance log
		\EndIf
		\EndIf
		\EndFor
		\State step $\gets$ step + $1$
		\EndWhile
	\end{algorithmic}
\end{algorithm}

@@

Heuristics often maintain a set of parameters that are used to control the behaviour of the heuristic. These parameters are refered to as heuristic \textit{state}. The concept of proxies arises from the sparsity of state as maintained by different heuristics. Since heuristics maintain (possibly) different states, there is an uncertainty of state transition when switching between heuristics. A solution to state indifference is to \textit{proxy} heuristic state update operations. State is then maintained in two parts: primary and proxied state. Primary state refers to the state that is originally maintained by a heuristic. Proxied state refers to the state that is not directly maintained by the heuristic, but can be updated by outsourcing the required state update operation to another heuristic. The \acs{BHH} thus incorporates a mapping of proxied state update operation as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}.

\begin{table}[htbp]
	\centering
	\caption{An example of a mapping of proxied state update operation maintained by the \acs{BHH}.}
	\label{tab:bhh:heuristic_pool:proxy_mapping_example}%
	\par\bigskip
	\resizebox{0.38\textwidth}{!}{
		\begin{tabular}{ccccc}
			                                                &   & \multicolumn{3}{c}{State Parameter}                                                                                                                                                                                      \\
			\cmidrule{3-5}                                  &   & 1                                                                      & 2                                                                      & 3                                                                      \\
			\cmidrule{3-5}    \multirow{3}[1]{*}{Heuristic} & A & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} \\
			                                                & B & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
			                                                & C & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
		\end{tabular}%
	}
\end{table}%

From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B for state parameter 2. Heuristic B will outsource from \index{heuristic}heuristic A for state parameter 3. Finally, \index{heuristic}heuristic C will outsource from \index{heuristic}heuristic A and B for state parameters 2 and 3 respectively. In this way, all \index{heuristic}heuristics maintain all the state parameters.

@@

The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit requirement $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha}; K)$, $\boldsymbol{\phi} \sim Dir(\boldsymbol{\beta}; K)^{J}$ and $\boldsymbol{\psi} \sim Beta(\gamma_{1}, \gamma_{0})$. In the aforementioned, $K$ is the heuristic pool size and $J$ is the entity pool size. The parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$ are referred to as concentration parameters. The concentration parameters parameterises the prior probability distributions. \ref{app:naive_bayes} provides mathematical derivations of the predictive model.

@@

Another approach to optimise the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ is to optimise the parameters by their probability distributions' parameters. This process is referred to as \textit{Bayesian analysis}. Bayesian analysis makes use of the \textit{posterior} probability distribution. The concentration update operations yielded by \acs{MAP} are given as follows:

@@

The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool as, the \textit{population size} specifies the number of entities in the entity pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, the \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on values assigned by the credit assignment strategies, backwards in the performance log.

@@

This section provides the details of the implementation of the empirical process. At a high level the experimental procedure consist of a comparison between the \acs{BHH} and standalone low-level heuristics. A number of datasets, models and heuristics are specified. Throughout the empirical process, the use of a \acs{BHH} baseline configuration is used.

@@

For the standalone heuristics experimental group, a number of low-level heuristics are used along with their specified hyper-parameters. Each of these standalone low-level heuristics are compared to that of the \acs{BHH} baseline configuration, across all datasets. The intent of the standalone heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level heuristics.

@@

\begin{table}[htb]
	\centering
	\caption{Classification datasets}
	\label{tab:methodology:datasets:classification}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{ccccccccc}
			\textbf{dataset} & \textbf{output} & \textbf{types}             & \textbf{attributes} & \textbf{classes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}          \\
			\midrule
			iris             & multivariate    & real                       & 4                   & 3                & 150                & 16             & 10             & \citep{ref:fisher:1936}    \\
			car              & multivariate    & categorical                & 6                   & 4                & 1728               & 128            & 14             & \citep{ref:bohanec:1988}   \\
			abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & \citep{ref:waugh:1995}     \\
			wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & \citep{ref:cortez:2009}    \\
			mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & \citep{ref:schlimmer:1987} \\
			bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & \citep{ref:moro:2014}      \\
			diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & \citep{ref:strack:2014}    \\
		\end{tabular}%
	}
\end{table}%

\begin{table}[htb]
	\centering
	\caption{Regression datasets}
	\label{tab:methodology:datasets:regression}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{cccccccc}
			\textbf{dataset}    & \textbf{output}           & \textbf{types} & \textbf{attributes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}         \\
			\midrule
			fish toxicity       & multivariate              & real           & 7                   & 908                & 64             & 15             & \citep{ref:cassotti:2015} \\
			housing             & univariate                & real           & 13                  & 506                & 32             & 16             & \citep{ref:harrison:1978} \\
			forest fires        & multivariate              & real           & 13                  & 517                & 32             & 17             & \citep{ref:cortez:2007}   \\
			student performance & multivariate              & integer        & 33                  & 649                & 32             & 21             & \citep{ref:cortez:2008}   \\
			parkinsons          & multivariate              & integer, real  & 26                  & 5875               & 256            & 23             & \citep{ref:tsanas:2009}   \\
			air quality         & multivariate, time series & real           & 15                  & 9358               & 256            & 37             & \citep{ref:de:2008}       \\
			bike                & univariate                & integer, real  & 16                  & 17389              & 256            & 68             & \citep{ref:fanaee:2014}   \\
		\end{tabular}%
	}
\end{table}%

@@

\begin{table}[htb]
	\centering
	\caption{Model configurations}
	\label{tab:methodology:models:configurations}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{rcccccccc}
			\textbf{dataset}    & \textbf{inputs} & \textbf{hidden} & \textbf{output} & \textbf{biases} & \textbf{parameters} & \textbf{topology} & \textbf{l1 activation} & \textbf{l2 activation} \\
			\midrule
			fish toxicity       & 6               & 3               & 1               & yes             & 25                  & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			iris                & 4               & 5               & 3               & yes             & 43                  & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			air quality         & 12              & 8               & 1               & yes             & 113                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			housing             & 13              & 8               & 1               & yes             & 121                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			wine quality        & 13              & 10              & 7               & yes             & 217                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			parkinsons          & 21              & 10              & 1               & yes             & 231                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			car                 & 21              & 10              & 4               & yes             & 264                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			forest fires        & 43              & 16              & 1               & yes             & 721                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			abalone             & 10              & 36              & 28              & yes             & 1432                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			bank                & 51              & 32              & 1               & yes             & 1697                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			bike                & 61              & 32              & 1               & yes             & 2017                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			student performance & 99              & 32              & 1               & yes             & 3233                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			adult               & 108             & 64              & 1               & yes             & 7041                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			mushroom            & 117             & 64              & 1               & yes             & 7617                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			diabetic            & 2369            & 32              & 3               & yes             & 75939               & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
		\end{tabular}%
	}
\end{table}%

@@

\begin{table}[htb]

@@

This appenfix aims to dissect the probabilistic model that is presented in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}. The \acs{BHH} implements a form of Naïve Bayes classifier, and thus independence between events can be assumed. The following derived \acp{PMF} are provided as fundamental building blocks to show the mechanism by which the \acs{BHH} learns.

>>>>

\usepackage{acro}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{url}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{multirow}

@@

\DeclareAcronym{BOHTA}{
      short = BOHTA,
      long = \textit{bi-objective hyperheuristic training algorithm}
}

@@

	\begin{abstract}
		The process of training \acfp{FFNN} can benefit from an automated process where the best heuristic to train the network is sought out automatically by means of a high-level probabilistic-based heuristic. This research introduces a novel population-based \acf{BHH} that is used to train \acfp{FFNN}. The performance of the \acs{BHH} is compared to that of ten popular low-level heuristics, each with different search behaviours. The chosen heuristic pool consists of classic gradient-based heuristics as well as \acfp{MH}. The empirical process is executed on fourteen datasets consisting of classification and regression problems with varying characteristics. The \acs{BHH} is shown to be able to train \acp{FFNN} well and provide an automated method for finding the best heuristic to train the \acp{FFNN} at various stages of the training process.
	\end{abstract}

@@

A popular field of focus for studying \acfp{ANN} is the process by which these models are trained. \acp{ANN} are trained by optimisation algorithms known as heuristics. Many different heuristics have been developed and used to train \acp{ANN} \citep{ref:rakitianskaia:2012}. Each of these heuristics has different search behaviours, characteristics, strengths and weaknesses. It is necessary to find the best heuristic to train \acp{ANN} in order to yield optimal results. This process is often non-trivial and time-consuming. Selection of the best heuristic to train \acp{ANN} is often problem specific \citep{ref:allen:1996}.

@@

The selection mechanism implemented by the \acs{BHH} is different from the \acf{AMALGAM} and \acf{BOHTA} methods used by \citet{ref:nel:2021}, as well as the \acf{HHBOA} proposed by \citet{ref:oliva:2019}. The key differences include that the \acs{BHH} does not follow an evolutionary approach to the selected low-level heuristics. As such the population does not generate offspring, but rather reuses entities in the population. Furthermore, the \acs{BHH} implements a discrete credit assignment mechanism, not making use of pareto fronts as in the \acs{AMALGAM} and \acs{BOHTA} methods.

@@

This research focuses on a particular type of \acs{ANN}, referred to as \acfp{FFNN}. \acp{FFNN} were the first and simplest type of \acp{ANN} developed \citep{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order. Furthermore, \acp{FFNN} implement fully connected topologies, where each \acf{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles \citep{ref:zell:1994}. In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.

@@

Gradient-based heuristics are optimisation techniques that make use of derivatives obtained from evaluating the \acs{ANN} error function. In the context of supervised learning, loss functions produce a scalar value that represents the error between the output of the \acs{ANN} and the desired output. When using \acf{GD} to train \acp{ANN}, the gradients of the loss function is used to adjust the weights of the \acs{ANN} in order to minimise the error \citep{ref:engelbrecht:2007}.

There are many variants of gradient-based heuristics. However, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}. This algorithm is known as \acf{BP}, was popularised by \citet{ref:werbos:1994}.

The simplest type of \acs{GD} algorithm is referred to as \acf{SGD}, which implements a gradient-based weight update step for each training pattern. In the context of this research, the implementation of \acs{SGD} refers to the mini-batch training implementation of \acs{GD}, where a small batch of training patterns are fed to the \acs{FFNN} at once and the error function is aggregated across all training patterns.

@@

Gradient-based heuristics are sensitive to the problem that they are applied to, with hyper-parameter selection often dominating the research focus \citep{ref:bengio:2000}. \citet{ref:blum:2003} mention that since the 1980s, a new kind of approximate algorithm has emerged which tries to combine basic heuristic methods in higher level frameworks aimed at efficiently and effectively exploring a search space. These methods are referred to as \acp{MH}.

@@

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include \citep{ref:burke:2010, ref:dowsland:2007, ref:grobler:2012, ref:vanderstockt:2018}. Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce. \citet{ref:nel:2021} provides some of the first research in this field, applying \acs{BOHTA}, a novel adaptation of an evolutionary-based \acs{HH}, known as the \acs{AMALGAM} \acs{HH} \citep{ref:vrugt:2007}, to \acs{FFNN} training. Furthermore, \citet{ref:oliva:2019} provide \acs{HHBOA}, the first use of Bayesian optimisation in a \acs{HH} context. The method proposed by \citet{ref:oliva:2019} uses a Bayesian selection operator to evolve combinations of low-level heuristics  while looking for good problem solutions to a benchmark of optimisation functions, but does not apply a \acs{HH} to the training of \acp{FFNN}.

@@

Bayesian analysis utilises the concept of conjugate priors. \citet{ref:wackerly:2014} state that conjugate priors are prior probability distributions that result in posterior distributions that are of the same functional form as the prior, but with different parameter values. The conjugate prior to a Bernoulli probability distribution is the Beta probability distribution and the conjugate prior to a categorical and multinomial probability distribution is the Dirichlet probability distribution \citep{ref:wackerly:2014}.

@@

This section presents the novel \acs{BHH}. The general concept of the \acs{BHH} is summarised as follows: the \acs{BHH} implements a high-level heuristic selection mechanism that learns to select the best heuristic from a pool of low-level heuristics. These low-level heuristics are applied to a population of entities, each implementing a candidate solution to a \acs{FFNN}. The  intent of the \acs{BHH} is to optimise both the underlying \acs{FFNN} and the \acs{FFNN} training process. The \acs{BHH} does so by learning the probability that a given heuristic will perform well at a given stage in the \acs{FFNN} training process. These probabilities are then used as heuristic selection probabilities in the next step of the training process.

According to the classification scheme for \acp{HH} by \citet{ref:burke:2010}, the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level heuristics in an online learning fashion. Figure \ref{fig:bhh_architecture} provides an illustration of the high-level architecture of the \acs{BHH}. Algorithm \ref{algo:bhh} provides the high level pseudo-code implementation of the \acs{BHH}. Discussions follow on the most important components of the \acs{BHH}.

@@

		\If {step $<$ replay window size}
		\State prune performance log
		\EndIf
		\EndIf
		\EndFor
		\State step $\gets$ step + $1$
		\EndWhile
	\end{algorithmic}
\end{algorithm}

@@

Heuristics often maintain a set of parameters that are used to control the behaviour of the heuristic. These parameters are refered to as heuristic \textit{state}. The concept of proxies arises from the sparsity of state as maintained by different heuristics. Since heuristics maintain (possibly) different states, there is an uncertainty of state transition when switching between heuristics. A solution to state indifference is to \textit{proxy} heuristic state update operations. State is then maintained in two parts: primary and proxied state. Primary state refers to the state that is originally maintained by a heuristic. Proxied state refers to the state that is not directly maintained by the heuristic, but can be updated by outsourcing the required state update operation to another heuristic. The \acs{BHH} thus incorporates a mapping of proxied state update operations as given in the example in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}.

\begin{table}[htbp]
	\centering
	\caption{An example of a mapping of proxied state update operation maintained by the \acs{BHH}.}
	\label{tab:bhh:heuristic_pool:proxy_mapping_example}%
	\par\bigskip
	\resizebox{0.38\textwidth}{!}{
		\begin{tabular}{ccccc}
			                                                &   & \multicolumn{3}{c}{State Parameter}                                                                                                                                                                                      \\
			\cmidrule{3-5}                                  &   & 1                                                                      & 2                                                                      & 3                                                                      \\
			\cmidrule{3-5}    \multirow{3}[1]{*}{Heuristic} & A & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} \\
			                                                & B & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
			                                                & C & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{n/a} & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{B}  & \cellcolor[rgb]{ 1,  .922,  .612}\textcolor[rgb]{ .612,  .341,  0}{A}  \\
		\end{tabular}%
	}
\end{table}%
\noindent
From the example given in Table \ref{tab:bhh:heuristic_pool:proxy_mapping_example}, when \index{heuristic}heuristic A is selected, it will outsource state update operations from \index{heuristic}heuristic B for state parameter 2. Heuristic B will outsource from \index{heuristic}heuristic A for state parameter 3. Finally, \index{heuristic}heuristic C will outsource from \index{heuristic}heuristic A and B for state parameters 2 and 3 respectively. In this way, all \index{heuristic}heuristics maintain all the state parameters.

@@

The predictive model thus models the \textit{proportional} probability of the event (selection of) heuristic $\boldsymbol{H}$, given allocation to entity $\boldsymbol{E}$ and credit requirement $\boldsymbol{C}$, parameterised by sampled $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha}; K)$, $\boldsymbol{\phi} \sim Dir(\boldsymbol{\beta}; K)^{J}$ and $\boldsymbol{\psi} \sim Beta(\gamma_{1}, \gamma_{0})$. In the aforementioned, $K$ is the heuristic pool size and $J$ is the entity pool size. The parameters $\boldsymbol{\alpha}$, $\boldsymbol{\beta}$, $\gamma_{1}$ and $\gamma_{0}$ are referred to as concentration parameters. The concentration parameters are used to parameterise the prior probability distributions. \ref{app:naive_bayes} provides mathematical derivations of the predictive model.

@@

\Acs{MAP} is an approach to optimise the values for $\hat{\theta}_{k}$, $\hat{\phi}_{j,k}$ and $\hat{\psi}_{k}$ by optimising the parameters of their probability distributions. This process is referred to as \textit{Bayesian analysis}. Bayesian analysis makes use of the \textit{posterior} probability distribution. The concentration update operations yielded by \acs{MAP}, are given as follows:

@@

The following hyper-parameters are implemented by the \acs{BHH}: the \textit{heuristic pool} configures the type of heuristics included in the heuristic pool, the \textit{population size} specifies the number of entities in the entity pool, the \textit{credit assignment strategy} specifies which credit assignment strategy to use, the \textit{reselection interval} determines the frequency of heuristic reselection, the \textit{replay window size} determines the maximum size of the performance log, the \textit{reanalysis interval} determines the frequency at which Bayesian analysis is applied, the \textit{burn in window size} determines the size of an initial window where experience is simply gathered without reanalysis, and finally, the \textit{discounted rewards} and \textit{normalisation} flags toggle scaling modifiers on values assigned by the credit assignment strategies, backwards in the performance log.

@@

This section provides the details of the implementation of the empirical process. At a high level the experimental procedure consist of a comparison between the \acs{BHH} and standalone low-level heuristics. A number of datasets, models and heuristics are specified. Throughout the empirical process, a \acs{BHH} baseline configuration is used.

@@

For the standalone heuristics experimental group, a number of low-level heuristics are used along with their specified hyper-parameters. Each of these standalone low-level heuristics is compared to that of the \acs{BHH} baseline configuration, across all datasets. The intent of the standalone heuristics experimental group is to determine if the \acs{BHH} baseline configuration can generalise to multiple problems in comparison to individual low-level heuristics.

@@

\begin{table}[!tb]
	\centering
	\caption{Classification datasets}
	\label{tab:methodology:datasets:classification}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{ccccccccc}
			\textbf{dataset} & \textbf{output} & \textbf{types}             & \textbf{attributes} & \textbf{classes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}          \\
			\midrule
			iris             & multivariate    & real                       & 4                   & 3                & 150                & 16             & 10             & \citep{ref:fisher:1936}    \\
			car              & multivariate    & categorical                & 6                   & 4                & 1728               & 128            & 14             & \citep{ref:bohanec:1988}   \\
			abalone          & multivariate    & categorical, integer, real & 8                   & 28               & 4177               & 256            & 17             & \citep{ref:waugh:1995}     \\
			wine quality     & multivariate    & real                       & 12                  & 11               & 4898               & 256            & 20             & \citep{ref:cortez:2009}    \\
			mushroom         & multivariate    & categorical                & 22                  & 2                & 8214               & 512            & 17             & \citep{ref:schlimmer:1987} \\
			bank             & multivariate    & real                       & 17                  & 2                & 45211              & 512            & 89             & \citep{ref:moro:2014}      \\
			diabetic         & multivariate    & integer                    & 55                  & 3                & 100000             & 1024           & 98             & \citep{ref:strack:2014}    \\
		\end{tabular}%
	}
\end{table}%

\begin{table}[!tb]
	\centering
	\caption{Regression datasets}
	\label{tab:methodology:datasets:regression}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{cccccccc}
			\textbf{dataset}    & \textbf{output}           & \textbf{types} & \textbf{attributes} & \textbf{instances} & \textbf{batch} & \textbf{steps} & \textbf{citation}         \\
			\midrule
			fish toxicity       & multivariate              & real           & 7                   & 908                & 64             & 15             & \citep{ref:cassotti:2015} \\
			housing             & univariate                & real           & 13                  & 506                & 32             & 16             & \citep{ref:harrison:1978} \\
			forest fires        & multivariate              & real           & 13                  & 517                & 32             & 17             & \citep{ref:cortez:2007}   \\
			student performance & multivariate              & integer        & 33                  & 649                & 32             & 21             & \citep{ref:cortez:2008}   \\
			parkinsons          & multivariate              & integer, real  & 26                  & 5875               & 256            & 23             & \citep{ref:tsanas:2009}   \\
			air quality         & multivariate, time series & real           & 15                  & 9358               & 256            & 37             & \citep{ref:de:2008}       \\
			bike                & univariate                & integer, real  & 16                  & 17389              & 256            & 68             & \citep{ref:fanaee:2014}   \\
		\end{tabular}%
	}
\end{table}%

@@

\begin{table}[!tb]
	\centering
	\caption{Model configurations}
	\label{tab:methodology:models:configurations}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{rcccccccc}
			\textbf{dataset}    & \textbf{inputs} & \textbf{hidden} & \textbf{output} & \textbf{biases} & \textbf{parameters} & \textbf{topology} & \textbf{l1 activation} & \textbf{l2 activation} \\
			\midrule
			fish toxicity       & 6               & 3               & 1               & yes             & 25                  & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			iris                & 4               & 5               & 3               & yes             & 43                  & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			air quality         & 12              & 8               & 1               & yes             & 113                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			housing             & 13              & 8               & 1               & yes             & 121                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			wine quality        & 13              & 10              & 7               & yes             & 217                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			parkinsons          & 21              & 10              & 1               & yes             & 231                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			car                 & 21              & 10              & 4               & yes             & 264                 & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			forest fires        & 43              & 16              & 1               & yes             & 721                 & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			abalone             & 10              & 36              & 28              & yes             & 1432                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			bank                & 51              & 32              & 1               & yes             & 1697                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			bike                & 61              & 32              & 1               & yes             & 2017                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			student performance & 99              & 32              & 1               & yes             & 3233                & dense             & LReLU ($\alpha = 0.3$) & sigmoid                \\
			adult               & 108             & 64              & 1               & yes             & 7041                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			mushroom            & 117             & 64              & 1               & yes             & 7617                & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
			diabetic            & 2369            & 32              & 3               & yes             & 75939               & dense             & LReLU ($\alpha = 0.3$) & softmax                \\
		\end{tabular}%
	}
\end{table}%

@@

\begin{table}[!tb]

@@

This section aims to dissect the probabilistic model that is presented in Equation~\eqref{eq:bhh:selection_mechanism:predictive_model_prop_to}. The \acs{BHH} implements a form of Naïve Bayes classifier, and thus independence between events can be assumed. The following derived \acp{PMF} are provided as fundamental building blocks to show the mechanism by which the \acs{BHH} learns.
